---
title: "A multi-task learning framework to uncover orthogonal feature interactions in large scale drug screening experiments"
author: "MI YANG"
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{Bioconductor style for PDF documents}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output: 
  BiocStyle::html_document
---


```{r include=FALSE, cache=FALSE}
path <- "~/Documents/RWTH_Aachen"
source(paste0(path,"/MACAU_PROJECT/interaction_matrix_Functions.R"))
source(paste0(path,"/FUNCTIONS/PLOT.R"))
source(paste0(path,"/FUNCTIONS/general_functions.R"))
target <- read.csv(paste0(path,"/macau_work_dir/macau_test_sanger/DATA/target"), check.names = F) ; drug_names <- target[ ,1] ; target <- target[ ,-1]
DRUG_ANALYSIS_SET_update$Drug.Name <- DRUG_ANALYSIS_SET$DRUG_NAME

target_to_remove <- c()
for (i in 1:length(colnames(target))) {
protein_target <- print_target_GDSC (protein_target= colnames(target)[i], target_matrix=target, drug_names=drug_names )
if ( length(protein_target[,1]) == 1 ) { target_to_remove <- c(target_to_remove, i) }
}
target_to_remove <- c(target_to_remove , which(colnames(target) %in% c("others","not defined" ))  ) 

tissue_label_gdsc <- read.csv(paste0(path,"/SANGER_DATA/tissue_label_gdsc_ID"), row.names=1)
table(tissue_label_gdsc$tissue) ; names(which(table(tissue_label_gdsc$tissue) > 20)) 
tissue <- c("aero_dig_tract","bone","brain","breast","colon","kidney","leukemia","liver","lung_NSCLC","lung_SCLC","lymphoma","ovary","pancreas","skin","soft_tissue","stomach")
#  print_target_GDSC ( protein_target= "ERBB2" , target_matrix=target, drug_names=drug_names )
```


# Target - Progeny interaction (conservative/all_target , Single/Absolute)

```{r echo=FALSE, cache=FALSE}
significance_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single")
save_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",significance=0.20)

significance_interaction_plot(drug_feature_name="target_Leiden",cell_feature_name="progeny11",selection="conservative",cut_off="single")
save_interaction_plot(drug_feature_name="target_Leiden",cell_feature_name="progeny11",selection="conservative",cut_off="single",significance=0.05)

significance_interaction_plot(drug_feature_name="target",cell_feature_name="SNP_CNV",selection="conservative",cut_off="single")
save_interaction_plot(drug_feature_name="target",cell_feature_name="SNP_CNV",selection="conservative",cut_off="single",significance=0.20)


## PAN CANCER
x <- read.csv("~/Documents/RWTH_Aachen/macau_work_dir/macau_test_sanger/DATA_RESULT_STORAGE/transduction/interaction_target_progeny11_IC50_fold_sample600_latent30.csv", row.names = 1)
rownames(x)[grep("G9a and GLP methyltransferases",rownames(x))] <- "G9a and GLP"
rownames(x)[grep("dsDNA break induction",rownames(x))] <- "dsDNA break"
x <- x[ - target_to_remove ,  ] ; mat <- x
mat <- subset_row_abs(mat, abs_limit = 0.95, obs=1) ;  v <- apply(mat,1,var) ;  v <- v[ order(-abs(v)) ] ; mat <- mat[ names(v)[1:25] , ]
v <- apply(mat,2,var) ;  v <- v[ order(-abs(v)) ]  
pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_PAN_CANCER_target_progeny11.pdf", sep = ""), width = 13 , height = 15, onefile = F )
plot_pheatmap(mat, row_names="Drug target", col_names="progeny11" , title="Pan cancer Target - Progeny11" ) 
dev.off()

## PAN CANCER
x <- read.csv("~/Documents/RWTH_Aachen/macau_work_dir/macau_test_sanger/DATA_RESULT_STORAGE/transduction/interaction_target_progeny14_IC50_fold_sample600_latent30.csv", row.names = 1)
rownames(x)[grep("G9a and GLP methyltransferases",rownames(x))] <- "G9a and GLP"
rownames(x)[grep("dsDNA break induction",rownames(x))] <- "dsDNA break"
x <- x[ - target_to_remove ,  ] ; mat <- x
mat <- subset_row_abs(mat, abs_limit = 0.95, obs=1) ;  v <- apply(mat,1,var) ;  v <- v[ order(-abs(v)) ] ; mat <- mat[ names(v)[1:25] , ]
v <- apply(mat,2,var) ;  v <- v[ order(-abs(v)) ]  
pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_PAN_CANCER_target_progeny14.pdf", sep = ""), width = 13 , height = 15, onefile = F )
plot_pheatmap(mat, row_names="Drug target", col_names="progeny14" , title="Pan cancer Target - Progeny14" ) 
dev.off()


```


# Target - Progeny interaction (conservative/all_target , Single/Absolute)

```{r echo=FALSE, cache=FALSE}
save_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",significance=0.20 )

```


# Target - Progeny interaction: Tissue Gaps analysis

```{r echo=FALSE, cache=FALSE}

mat_list <- retrieve_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",tissue_name =  tissue) [[1]]
x <- mat_list[[1]]

coord_value_table <- c()
across_tissue_value <- c()
for(t in 1:length(rownames(x))) {
  for(p in 1:length(colnames(x))) {
    across_tissue <- c()
    for(i in 1:length(mat_list)) {
      x <- mat_list[[i]]
      across_tissue <- c(across_tissue, x[t,p])
    }
    across_tissue_value <- rbind(across_tissue_value, across_tissue)
    coord_value_table <- rbind(coord_value_table,c(t,p, signif(max(across_tissue)-min(across_tissue), digits = 3) ))
  }
}

colnames(coord_value_table) <- c("target","pathway", "Max_Min_GAP")
colnames(across_tissue_value) <- tissue
rownames(across_tissue_value) <- 1:length(rownames(across_tissue_value))
boxplot( coord_value_table[,3] ) 
boxplot( t(across_tissue_value) ) 

subset <- coord_value_table[coord_value_table[ ,3] > 0.8 , ]
for(i in 1:length(subset[,1])) {  
  subset[i, 1] <- rownames(x)[as.numeric(subset[i, 1])]
  subset[i, 2] <- colnames(x)[as.numeric(subset[i, 2])]   
}

subset_across_tissue_value <- across_tissue_value[ coord_value_table[ ,3] > 0.8 , ]
max(subset_across_tissue_value[1,])-min(subset_across_tissue_value[1,])
maxmin_tissue <- c()
maxmin_value <- c()
for(i in 1:length(subset[,1])) {  
 maxmin_tissue <- rbind( maxmin_tissue , c(names(which.max(subset_across_tissue_value[i,])), names(which.min(subset_across_tissue_value[i,]))) )
 maxmin_value <- rbind( maxmin_value , c(signif(max(subset_across_tissue_value[i,]), digits = 3), signif(min(subset_across_tissue_value[i,]), digits = 3)) )
}
colnames(maxmin_tissue) <- c("Max_tissue", "Min_tissue")
colnames(maxmin_value) <- c("Max_value", "Min_value")

subset <- cbind(subset, maxmin_tissue, maxmin_value)
subset <- subset[ ,c( "pathway","target","Max_tissue", "Min_tissue","Max_value", "Min_value","Max_Min_GAP")]

absolute_sum <- abs(as.numeric(subset[ ,5]) + as.numeric(subset[ ,6]))
subset <- cbind(subset, absolute_sum)
subset <- subset[ subset[ ,8] < 0.2 , ]
```


# Cross tissue interaction of target-progeny: CONVERGENT/DIVERGENT interactions

```{r echo=FALSE, cache=FALSE}

mat_list <- retrieve_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",tissue_name =  tissue) [[1]]
pvalue_list <- retrieve_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",tissue_name =  tissue) [[2]]

pvalue_tissue <- c()
for(i in 1:length(pvalue_list)) {
x <- pvalue_list[[i]]
y <- stack(x) ; ind2 <- rep( rownames(x) , length(colnames(x)) ) ; y <- cbind(y, ind2) ; rownames(y) <- paste0(y$ind,"_",y$ind2)  
pvalue_tissue <- cbind(pvalue_tissue, y$values)
}
rownames(pvalue_tissue) <- rownames(y) ; colnames(pvalue_tissue) <- tissue

mat_tissue <- c()
for(i in 1:length(mat_list)) {
x <- mat_list[[i]]
y <- stack(x) ; ind2 <- rep( rownames(x) , length(colnames(x)) ) ; y <- cbind(y, ind2) ; rownames(y) <- paste0(y$ind,"_",y$ind2)  
mat_tissue <- cbind(mat_tissue, y$values)
}
rownames(mat_tissue) <- rownames(pvalue_tissue) ; colnames(mat_tissue) <- tissue

mat_tissue <- scale(mat_tissue) ## scale by tissue !!!


library(pheatmap)
library(RColorBrewer)
# Sets the minimum (0), the maximum (15), and the increasing steps (+1) for the color scale
# Note: if some of your genes are outside of this range, they will appear white on the heatmap
breaksList = seq(-7, 7.5, by = 0.5)

library(pheatmap) ; library(grid)
plot_pheatmap <- function(mat, row_names, col_names , title ,cluster_rows=T,cluster_cols=T,fontsize=25,fontsize_row=25, fontsize_col=25, scale="none") {
  setHook("grid.newpage", function() pushViewport(viewport(x=1,y=1,width=0.9, height=0.95, name="vp", just=c("right","top"))), action="prepend")
  pheatmap(mat,color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(length(breaksList)), breaks = breaksList, main=title, fontsize=fontsize, fontsize_row=fontsize_row,fontsize_col=fontsize_col,cluster_rows = cluster_rows, cluster_cols = cluster_cols,scale=scale,display_numbers = matrix(ifelse(pvalue < 0.20, "*", ""), nrow(pvalue)))
  setHook("grid.newpage", NULL, "replace")
  grid.text(row_names, x=-0.03, rot=90, gp=gpar(fontsize=30))
  grid.text(col_names, y=0.01, gp=gpar(fontsize=30)  )
}

mat <- mat_tissue ; mat <- subset_row_abs(mat, abs_limit = 0.95, obs=1) ;  v <- apply(mat,1,mean) ;  v <- v[ order(-v) ] ; mat <- mat[ names(v)[1:30] , ]
pvalue <- pvalue_tissue[rownames(mat), ]
rownames(mat)[rownames(mat)=="Hypoxia_G9a and GLP methyltransferases"] <- "Hypoxia_G9a/GLP"

pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_TISSUE_target_progeny11_Sensitive.pdf", sep = ""), width = 15 , height = 16, onefile = F )
plot_pheatmap(mat, row_names="Pathway-Target pairs", col_names="Tissue" , title="Highest interactions" ) 
dev.off()

mat <- mat_tissue ; mat <- subset_row_abs(mat, abs_limit = 0.95, obs=1) ;  v <- apply(mat,1,var) ;  v <- v[ order(-v) ] ; mat <- mat[ names(v)[1:30] , ]
pvalue <- pvalue_tissue[rownames(mat), ]
rownames(mat)[rownames(mat)=="Hypoxia_G9a and GLP methyltransferases"] <- "Hypoxia_G9a/GLP"

pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_TISSUE_target_progeny11_Divergence.pdf", sep = ""), width = 15 , height = 16, onefile = F )
plot_pheatmap(mat, row_names="Pathway-Target pairs", col_names="Tissue" , title="Divergent interactions" ) 
dev.off()
 

```


# Cross tissue interaction of target-SNP/CNV: CONVERGENT/DIVERGENT interactions

```{r echo=FALSE, cache=FALSE}

mat_list <- retrieve_interaction_plot("target","SNP_CNV",selection="conservative",cut_off="single",tissue_name =  tissue) [[1]]
pvalue_list <- retrieve_interaction_plot("target","SNP_CNV",selection="conservative",cut_off="single",tissue_name =  tissue) [[2]]

all_gene <-  c() ; for(i in 1:length(mat_list)) { all_gene <- c(all_gene, colnames(mat_list[[i]])) } ;  all_gene <- unique(all_gene) ; all_gene <- all_gene[order(all_gene)]

mat_tissue <- c()
for(i in 1:length(mat_list)) {
  x <- mat_list[[i]]
  not_present <- setdiff(all_gene, colnames(x))
  not_present_mat <- matrix(ncol = length(not_present) , nrow = length(rownames(x)) ) ; colnames(not_present_mat) <- not_present ; rownames(not_present_mat) <- rownames(x)
  x <- cbind(x , not_present_mat) ; x <- x[ ,order(colnames(x))]
  
  y <- stack(x) ; ind2 <- rep( rownames(x) , length(colnames(x))) ; y <- cbind(y, ind2) ; rownames(y) <- paste0(y$ind,"_",y$ind2)  
  mat_tissue <- cbind(mat_tissue, y$values)
}
rownames(mat_tissue) <- rownames(y) ; colnames(mat_tissue) <- tissue

mat_tissue <- scale(mat_tissue) ## scale by tissue !!!
min(mat_tissue, na.rm=T) ; max(mat_tissue, na.rm=T) ; mean(mat_tissue, na.rm=T)

library(pheatmap)
library(RColorBrewer)
# Sets the minimum (0), the maximum (15), and the increasing steps (+1) for the color scale
# Note: if some of your genes are outside of this range, they will appear white on the heatmap
breaksList = seq(-40, 40, by = 1)

library(pheatmap) ; library(grid)
plot_pheatmap <- function(mat, row_names, col_names , title ,cluster_rows=T,cluster_cols=T,fontsize=25,fontsize_row=25, fontsize_col=25, scale="none") {
  setHook("grid.newpage", function() pushViewport(viewport(x=1,y=1,width=0.9, height=0.95, name="vp", just=c("right","top"))), action="prepend")
  pheatmap(mat,color = colorRampPalette(rev(brewer.pal(n = 7, name = "RdYlBu")))(length(breaksList)), breaks = breaksList, main=title, fontsize=fontsize, fontsize_row=fontsize_row,fontsize_col=fontsize_col,cluster_rows = cluster_rows, cluster_cols = cluster_cols,scale=scale,display_numbers=matrix(ifelse(pvalue < 0.20, "*", ""), nrow(pvalue)))
  setHook("grid.newpage", NULL, "replace")
  grid.text(row_names, x=-0.03, rot=90, gp=gpar(fontsize=30))
  grid.text(col_names, y=0.01, gp=gpar(fontsize=30)  )
}


mat <- mat_tissue ; mat[is.na(mat)] <- -41 ;  v <- apply(mat,1,mean) ;  v <- v[ order(-v) ] ; mat <- mat[ names(v)[1:30] , ]
rownames(mat)[rownames(mat)=="Hypoxia_G9a and GLP methyltransferases"] <- "Hypoxia_G9a/GLP"
pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_TISSUE_target_SNP_CNV_Sensitive.pdf", sep = ""), width = 22 , height = 16, onefile = F )
plot_pheatmap(mat, row_names="SNP/CNV-Target pairs", col_names="Tissue" , title="Highest interactions" ) 
dev.off()


mat <- mat_tissue ; mat[is.na(mat)] <- -13 
mat <- subset_row_up(mat, up_limit = 0.99, obs=1) ;  v <- apply(mat,1,var) ;  v <- v[ order(-v) ] ; mat_up <- mat[ names(v)[1:15] , ] ; mat_up[mat_up==-13] <- 41
mat <- mat_tissue ; mat[is.na(mat)] <- 41
mat <- subset_row_down(mat, down_limit = 0.01, obs=1) ;  v <- apply(mat,1,var) ;  v <- v[ order(-v) ] ; mat_down <- mat[ names(v)[1:15] , ]
mat <- rbind(mat_up,mat_down)


all_gene <-  c() ; for(i in 1:length(pvalue_list)) { all_gene <- c(all_gene, colnames(pvalue_list[[i]])) } ;  all_gene <- unique(all_gene) ; all_gene <- all_gene[order(all_gene)]
pvalue_tissue <- c()
for(i in 1:length(pvalue_list)) {
  x <- pvalue_list[[i]]
  not_present <- setdiff(all_gene, colnames(x))
  not_present_mat <- matrix(ncol = length(not_present) , nrow = length(rownames(x)) ) ; colnames(not_present_mat) <- not_present ; rownames(not_present_mat) <- rownames(x)
  x <- cbind(x , not_present_mat) ; x <- x[ ,order(colnames(x))]
  
  y <- stack(x) ; ind2 <- rep( rownames(x) , length(colnames(x))) ; y <- cbind(y, ind2) ; rownames(y) <- paste0(y$ind,"_",y$ind2)  
  pvalue_tissue <- cbind(pvalue_tissue, y$values)
}
rownames(pvalue_tissue) <- rownames(y) ; colnames(pvalue_tissue) <- tissue

pvalue <- pvalue_tissue[rownames(mat), ] ; pvalue[is.na(pvalue)] <- 1 

pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_TISSUE_target_SNP_CNV_Divergence.pdf", sep = ""), width = 20 , height = 16, onefile = F )
plot_pheatmap(mat, row_names="SNP/CNV-Target pairs", col_names="Tissue" , title="Divergent interactions" ) 
dev.off()

```


# Cross tissue interaction of target-progeny: SIGN CONSISTENCY 

```{r echo=FALSE, cache=FALSE}

# mat <- mat_tissue ; mat <- subset_row_abs(mat, abs_limit = 0.95, obs=1)

mat_tissue_sign <- mat_tissue
mat_tissue_sign[mat_tissue_sign > 0] <- 1
mat_tissue_sign[mat_tissue_sign < 0] <- -1
sign <- c()
for(i in 1:length(mat_tissue_sign[ ,1])) {
  sign_plus <- length(which(mat_tissue_sign[i, ]==1))
  sign_minus <- length(colnames(mat_tissue_sign)) - sign_plus
  sign <- rbind(sign, c(sign_plus,sign_minus))
}
mat_tissue_sign <- cbind(sign,mat_tissue_sign) ; 

hist(mat_tissue_sign[ ,1])

```


# Target - GEX interaction (conservative/all_target , Single/Absolute)

```{r echo=FALSE, cache=FALSE}
## not working, rerun macau on target-GEX
save_interaction_plot("target","GEX",selection="conservative",cut_off="single"  ,limit_col=0.999)

## PAN CANCER
path <- "/Users/miyang/Documents/RWTH_Aachen/macau_work_dir/macau_test_sanger/DATA_RESULT_STORAGE/transduction/"
x <- read.csv(paste(path,"interaction_target_GEX_IC50_fold_sample600_latent30.csv",sep=""),row.names=1)
GEX_ALL_names <- read.csv("~/Documents/RWTH_Aachen/macau_work_dir/macau_test_sanger/ORIGINAL_DATA/GEX_ALL_names", row.names=1); GEX_ALL_names$x <- as.character(GEX_ALL_names$x)
colnames(x) <- GEX_ALL_names$x
x <- x[ - target_to_remove ,  ]  
mat <- x
mat <- subset_col_abs(mat, abs_limit = 0.999, obs=1) 
v <- apply(mat,2,var) ;  v <- v[ order(-abs(v)) ] ; mat <- mat[ , names(v)[1:30] ]
v <- apply(mat,1,var) ;  v <- v[ order(-abs(v)) ] ; mat <- mat[ names(v)[1:20] , ]

pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/interaction_PAN_CANCER_target_GEX.pdf", sep = ""), width = 20 , height = 13, onefile = F )
plot_pheatmap(mat, row_names="Drug target", col_names="GEX" , title="Pan cancer Target - GEX" )
dev.off()
```


# Target - Transcription factor activity interaction

```{r echo=FALSE, cache=FALSE}
save_interaction_plot("target","TF_score",selection="conservative",cut_off="single")

```

# Target - SNP CNV interaction

```{r echo=FALSE, cache=FALSE}
path <- "/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/target_SNP_CNV/" 
setwd(path) ; f <- list.files(path) ; data_folder <- list.files("/Users/miyang/Documents/RWTH_Aachen/SANGER_DATA/TISSUE" )

for(i in 1:length(f)) {
x <- read.csv(f[i], row.names=1) ; x <- x[ - target_to_remove ,  ] 
to_remove <- read.csv(paste("/Users/miyang/Documents/RWTH_Aachen/SANGER_DATA/TISSUE/",data_folder[i],"/SNP_CNV_to_Remove",sep=""), row.names=1)
x <- x[ ,-which(colnames(x) %in% to_remove$x)] ; mat <- x
s <- rowSums(mat) ; s <- s[ order(-abs(s)) ] ; mat <- mat[ names(s)[1:25] , ]
s <- rowSums(mat) ; s <- s[ order(-abs(s)) ] ; mat <- mat[ names(s)[1:20] , ]

tissue <- regmatches(f[i], regexpr('interaction.+?target', f[i])) ; tissue <- gsub('.{7}$', '', tissue) ; tissue <- substring(tissue, 13)
pdf(paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/PLOTS/GDSC_Target_SNP_CNV/", tissue ,".pdf", sep = ""), width = 22 , height = 18, onefile = F )
plot_pheatmap(mat,"Drug target" , "SNP + CNV" , paste("Target - SNP_CNV (",tissue,")",sep = "")  ) 
dev.off()
}
```

# Target - GSVA Reactome interaction 

```{r echo=FALSE, cache=FALSE}
save_interaction_plot("target","GSVA_Reactome",selection="conservative",cut_off="single")

```

# Quality Control for GDSC

```{r echo=FALSE, cache=FALSE}
SEED_chosen  <- "SEED_RANDOM"
list_of_name <- c("target_GEX","target_progeny11","target_SNP_CNV")

result_table <- c()
for(feature in 1:length(list_of_name)) {
path <- paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/summary_QC/",SEED_chosen,"/",list_of_name[feature],"_QC/" ,sep = "" ) 
setwd(path) ; f <- list.files(path)  
mean <- c()
sd <- c()
for(i in 1:length(f)) {
  x <- list.files( paste(path, f[i],sep="") ) 
  x <- strsplit(x, "=") ; 
  mean <- c(mean, x[[1]][2] ) # take the mean pearson correlation
  sd <- c(sd, x[[length(x)]][2] ) # take the sd pearson correlation
}
result_table <- cbind( result_table, paste0(as.character(mean)," (sd=",as.character(sd),")" ) )  
}
rownames(result_table) <- f ; colnames(result_table) <- list_of_name
write.csv(result_table, paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/summary_QC/",SEED_chosen,"_TABLE", sep = "")  )

# describe this table, according to sample size, some tissues need further investigations. 
```

# Quality Control for CTRP2

```{r echo=FALSE, cache=FALSE}
list_of_name <- c("target_GEX","target_progeny11")

result_table <- c()
for(feature in 1:length(list_of_name)) {
path <- paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_CCLE/",list_of_name[feature],"_QC/" ,sep = "" ) 
setwd(path) ; f <- list.files(path)  
mean <- c()
sd <- c()
for(i in 1:length(f)) {
  x <- list.files( paste(path, f[i],sep="") ) 
  x <- strsplit(x, "=") ; 
  mean <- c(mean, x[[1]][2] ) # take the mean pearson correlation
  sd <- c(sd, x[[length(x)]][2] ) # take the sd pearson correlation
}
result_table <- cbind( result_table, paste0(as.character(mean)," (sd=",as.character(sd),")" ) )  
}
rownames(result_table) <- f ; colnames(result_table) <- list_of_name
write.csv(result_table, paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/summary_QC/",SEED_chosen,"_TABLE", sep = "")  )

# describe this table, according to sample size, some tissues need further investigations. 
```


# COMPARING GDSC and CTRP2
```{r echo=FALSE, cache=FALSE}

tissue_to_compare <- "skin"

GDSC <- read.csv(paste0("~/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/target_progeny11/interaction_",tissue_to_compare,"_target_progeny11_sample600_latent30.csv"), row.names=1)
GDSC <- GDSC[-target_to_remove, ]
GDSC_pvalue_CORRECTED <- read.csv(paste0("~/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/target_progeny11_PERMUTATION/",tissue_to_compare,"/interaction_pvalue_CORRECTED"), row.names=1)


CTRP <- read.csv(paste0("~/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_CTRP/target_progeny11/interaction_",tissue_to_compare,"_target_progeny11_sample600_latent30.csv"), row.names=1)

target_CTRP <- read.csv("~/Documents/RWTH_Aachen/CTD2/target",row.names = 1,check.names = F)
target_to_remove_CTRP <- c()
for (i in 1:length(colnames(target_CTRP))) {
protein_target <- print_target_CTRP (protein_target= colnames(target_CTRP)[i], target_matrix=target_CTRP, drug_names=rownames(target_CTRP) )
if ( length(protein_target[,1]) == 1 ) { target_to_remove_CTRP <- c(target_to_remove_CTRP, i) }
}
CTRP <- CTRP[-target_to_remove_CTRP, ]

# significance_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single", database = "CTRP",target_to_remove=target_to_remove_CTRP)
CTRP_pvalue_CORRECTED <- read.csv(paste0("~/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_CTRP/target_progeny11_PERMUTATION/",tissue_to_compare,"/interaction_pvalue_CORRECTED"), row.names=1)

common <- intersect(rownames(GDSC),rownames(CTRP))

GDSC <- GDSC[common, ]
CTRP <- CTRP[common, ]

x <- corr_by_row(t(GDSC), t(CTRP))
cor.test(as.numeric(data.matrix(GDSC)),as.numeric(data.matrix(CTRP)))


########################### compare the significant ones ###########################
GDSC_pvalue_CORRECTED <- GDSC_pvalue_CORRECTED[common, ]
CTRP_pvalue_CORRECTED <- CTRP_pvalue_CORRECTED[common, ]

common <- intersect(names(which(rowSums(GDSC_pvalue_CORRECTED==1) < 6) ), names(which(rowSums(CTRP_pvalue_CORRECTED==1) < 6) ))
GDSC <- GDSC[common, ]
CTRP <- CTRP[common, ]

x <- corr_by_row(t(GDSC), t(CTRP))
cor.test(as.numeric(data.matrix(GDSC)),as.numeric(data.matrix(CTRP)) )


```



# Significance test

```{r echo=FALSE, cache=FALSE}
SEED_chosen  <- "SEED_RANDOM"
# list_of_name <- c("target_GEX","target_progeny11","target_SNP_CNV")
# list_of_name <- c("target_GEX","target_progeny11")
# list_of_name <- c("target_progeny11","target_SNP_CNV")
# list_of_name <- c("target_GEX","target_SNP_CNV")

anova_result <- c()
for(t in 1:length(f)) {
  correlation_table <- c()
  for(feature in 1:length(list_of_name)) {
    path <- paste("/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/TISSUE_SPECIFIC_GDSC/summary_QC/",SEED_chosen,"/",list_of_name[feature],"_QC/" ,sep = "" ) 
    setwd(path) ; f <- list.files(path)  
    x <- list.files( paste(path,f[t],sep="") , pattern="^pcorr") 
    correlation <- c()
    for(i in 1:length(x)) { 
      c <- read.csv(paste(path,f[t],"/",x[i],sep=""),row.names = 1) 
      correlation <- c(correlation, c$X0)
    }
    correlation_table <- cbind(correlation_table,correlation)
  }
  colnames(correlation_table) <- list_of_name
  
  ## ANOVA test  https://www.stat.wisc.edu/~yandell/st571/R/anova.pdf
  y <- c()
  for(i in 1:length(colnames(correlation_table))) {
    y = c(y,correlation_table[,i])
  }
  n = rep(length(correlation_table[,1]),length(colnames(correlation_table)))
  group = rep(1:length(colnames(correlation_table)), n)
  data = data.frame(y = y, group = factor(group))
  fit = lm(y ~ group, data)
  result <- anova(fit)
  anova_result <- c(anova_result , result$`Pr(>F)`[1])
}
anova_result <- cbind(f,anova_result) ; anova_result

```


# Pubmed mining of associations

```{r echo=FALSE, cache=FALSE}
result_folder <- "/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/Pubmed/TISSUE_SPECIFIC_GDSC/"

tissue <- c("aero_dig_tract","bone","brain","breast","colon","kidney","leukemia","liver","lung_NSCLC","lung_SCLC","lymphoma","ovary","pancreas","skin","soft_tissue","stomach")
tissue_Pubmed <- c("aerodigestive tract","bone","brain","breast","colon","kidney","leukemia","liver","NSCLC","SCLC","lymphoma","ovary","pancreas","skin","soft tissue","stomach")

mat_list <- retrieve_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",tissue_name =  tissue) [[1]]

for(i in 1:16) {
  x <- mat_list[[i]]
  result <- find_pubmed_association(rownames(x), colnames(x), tissue_Pubmed[i])
  write.csv(result, paste0(result_folder,tissue[i]))
}

## ANALYSIS RESULT
mat_list <- retrieve_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",tissue_name =  tissue) [[1]]
pvalue_list <- retrieve_interaction_plot(drug_feature_name="target",cell_feature_name="progeny11",selection="conservative",cut_off="single",tissue_name =  tissue) [[2]]

setwd(result_folder) ; f <- list.files(result_folder)
result_table <- c()
for(i in 1:length(f)) {  ##  i  =  4
  pubmed <- read.csv(f[i], row.names = 1) ; pubmed <- as.numeric(data.matrix(pubmed))
  mat <- mat_list[[i]] ; mat <- as.numeric(data.matrix(mat))
  pvalue <- pvalue_list[[i]] ; pvalue <- as.numeric(data.matrix(pvalue))
  result <- cbind(mat,pvalue,pubmed)
  result <- result[-1, ]  # remove EGFR/EGFR becasue same name protein and pathway
  result <- result[which(result[ ,2]<1), ] ## remove p value of 1
  result[ ,1] <- abs(result[ ,1])
  result <- result[ which(result[ ,3] > 0), ] ## remove Pubmed count null
#  result[ ,3] <- log10(result[ ,3])
  
  corr <- cor.test(result[, 1],result[ ,3]) ; 
  t<- c(corr$estimate,corr$p.value)
  result_table <- rbind(result_table, t)
#  scatter_plot(result[ ,c(1,3)], title=tissue[i], "Absolute interaction weight", "Pubmed count")
}
rownames(result_table) <- tissue
colnames(result_table) <- c("correlation","p-value")
adj_p_value <- p.adjust( result_table[ ,2] , method = "fdr" ) 
result_table <- cbind(result_table, adj_p_value)
result_table <- signif(result_table, 3)

result_folder <- "/Users/miyang/Documents/RWTH_Aachen/MACAU_PROJECT/DATA_RESULT_STORAGE/Pubmed/"
write.csv(result_table, paste0(result_folder,"Pubmed_target_pathway_tissue_specific"))

```













